%-------------------------
% Resume in Latex
% Author : Henok Keflu 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[8]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{8pt}
      \textbf{#1} & \textit{#2} \\
       \vspace{3pt}
      \textbf{#3} & \textit{#4} \\
       \vspace{3pt}
      \textbf{#5} & \textit{#6} \\
       \vspace{3pt}
      \textbf{#7} & \textit{#8} \\
      % \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Henok Keflu} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:905314204536}{+1 647 710 4142}
    $|$
    \faAt \hspace{.5pt} \href{mailto:kefluhenok@gmail.com}{kefluhenok@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/heniam}{/heniam}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/heniam}{/heniam}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps?cid=15832573594118352153}{Toronto, Ontario }
\end{center}



%----------- EDUCATION -----------

\section{Education \& Certification }
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {B.Sc. in Computer Science \textbf{--} \normalfont{\textit {York University} }
      } 
      {Sep 2015 \textbf{--} Feb 2020}
      {Full-Stack Web Development with React Specialization \textbf{--} \normalfont{\textit {Coursera} }
      } {May 2020}
      {Cloud Development Nanodegree \textbf{--} 
      \normalfont{\textit {Udacity}
      }}{Dec 2020}  
      {Advanced Angular  \textbf{--} \normalfont{\textit {Angular Academy}
      }} {Jan 2021}
  \resumeSubHeadingListEnd



%----------- Technical Skills -----------

\section{Technical Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
    
        \textbf{Languages:}{ C/C++, C\#, TypeScript, Java, Swift, GraphQL, Unix Shell, WebGL, Python, JavaScript, SQL, MATLAB} \\ \vspace{3pt}

        \textbf{Technologies:}{     Agile Development, RESTful API, AWS, Azure, Docker, CI/CD, Travis CI, Kubernetes, Eclipse, \\ \hspace{67.5pt}Git, Wireshark, Scapy, Kali Linux, Network Security} \\ \vspace{3pt}
        
        \textbf{Libraries:}{ React, React Native, Angular, Vue, SASS, HTML/CSS, NodeJS, Selenium, Express, MySQL, MongoDB, \\ \hspace{51.5pt}DB2, Splunk, New Relic  } \\ \vspace{3pt}
    
    }}
  \resumeSubHeadingListEnd



%----------- Professional Experience -----------

\section{Professional Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer, Full Stack}{}
      {Lyceum Health}{Jul 2021 \textbf{--} Present, Full-time}
        \resumeItemListStart
            \resumeItem{Develop and sustain the application's front end for a smooth user experience with responsive and intuitive interfaces.}
            \resumeItem{Employ diverse programming languages, frameworks, and libraries for building robust and efficient applications. }
             \resumeItem {Implement code review and version control best practices for improved team efficiency.}
        \resumeItemListEnd

    \resumeSubheading
      {Production Support Engineer}{}
      {Cox Automotive Canada}{Apr 2021 \textbf{--} Feb 2022, Full-time}
        \resumeItemListStart
            \resumeItem{Proactively monitor and respond to incidents in production systems and applications for seamless operations.}
            \resumeItem{Participate in on-call rotations, providing support based on organizational needs and system criticality.}
            \resumeItem{ Efficiently manage interactions with third-party vendors and troubleshoot issues to ensure smooth operations.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Software Developer, Full Stack}{}
      {Changes On the Fly}{Dec 2020 \textbf{--} Mar 2021, Contract }
        \resumeItemListStart
            \resumeItem{Stay abreast of industry trends and emerging technologies, incorporating relevant tools and practices into the development process.}
            \resumeItem{Leveraged knowledge in full stack development, using MEAN stack and debugged using chrome.}
            \resumeItem{Conduct thorough testing and debugging to identify and resolve issues, ensuring the delivery of high-quality software.}
        \resumeItemListEnd   
        
   \resumeSubheading
      {Software Developer, Full Stack}{}
      {Self Employed}{Sep 2019 \textbf{--} Present, Freelance }
        \resumeItemListStart
            \resumeItem{Stay abreast of industry trends and emerging technologies, incorporating relevant tools and practices into the development process.}
            \resumeItem{Responsible developing dynamic and responsive web applications and mobile apps using Angular, React, React Native, Expo and Swift for a soothing function to allow for a user-friendly experience.}
            % \resumeItem{Conduct thorough testing and debugging to identify and resolve issues, ensuring the delivery of high-quality software.}
        \resumeItemListEnd    
        
  \resumeSubHeadingListEnd






%----------- Projects -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ristorante Con fusion \textbf{--} \normalfont{\textit{Coursera}}}{}{}{}
      \vspace{-16pt}
        \resumeItemListStart
            \resumeItem{ Developed a Multiplatform application using React Native, that allows users to rate and review plates.}
            \resumeItem{Utilized React Native, MongoDB, React.js Libraries, Caching, Local Persistent Data}
        \resumeItemListEnd
    
    \vspace{8pt}
    
    \resumeSubheading
      {Udagram \textbf{--} \normalfont{\textit{Udacity}}}{}{}{}
      \vspace{-16pt}
        \resumeItemListStart
            \resumeItem{Developed a clone of Instagram using basic Angular as front end and AWS cloud as its back end.}
            \resumeItem{Created a basic login page which validates authentication using basic Node and Express.}
             \resumeItem{Utilized AWS EC2, CloudFront, S3 Bucket, Docker, Travis Ci, CI/CD, Kubernetes, Terminal and Git..}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}